---
title: "Example document"
author: "Yours truly"
date: "Right here, right now"
output:
  html_document: default
  pdf_document: default
  word_document: default
bibliography: "bilbiography.bib"
---

*asdf* **strong emphasis** asdfd  sdfd

As Weiner et al. mentioned @weiner2018metabolite ...


 $$\sum_{i=1}^n (x_i - x)^2$$


|table  | with  | pipes|
|-------|-------|------|
|do it  | with  |     R|

```{r}
summary(iris)
```


# Water lilies analysis

There is a lake in a garden. Every day, the water lilies cover twice as much area as the previous day. On the first day, the water lilies cover 1/100th of the area of the lake.

What is the formula to calculate the area covered by the water lilies on day n? (pen and paper, not in Rstudio!)

 $$A_n = A_{n-1} \cdot 2$$

 $$A(n) = \frac{1}{100} \cdot 2^{n-1}$$
assign days 1 … 10 to variable x. Now assign the fraction of the area covered by water lilies on day n to variable y

```{r}
days <- 1:10
area <- 1/100 * 2^(days - 1)
```


plot x vs y (use the simple plot(x, y) function)


```{r}
plot(days, area)
abline(h=.5)
```

When will the half of the area be covered by water lilies? Use abline(h=.5) (what does it do?) to show a graphical solution
What is the fraction on day 3? Hint: what does y[3] do?
Speaking of which, what dows y[4:5] do? (just try it!)
Make the plot yourself.
use ‘col’ parameter of plot and a color name (e.g. “red”) to change the color of the line (plot(..., col="red"))
what if each day the lilies cover a fraction of area that is 1.5 the fraction of area on the previous day?
Use lines(x, y) function to put a second line on the plot



